### 2018-12-28 Sections/state_of_the_art.tex
indexing
Formatting update

Optical waveguides can be miniaturised and integrated onto a small chip, which is alignment-free, compact, and phase-stable\index{Phase-stability}.

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		Atom-light interaction currently represents the most mature method to create atomic squeezing, and owns the highest squeezing of 20.1 dB via an optical-cavity-based measurement. & \cite{bib:hosten2016measurement} \\
		\hline
		The detection of a single photon prepares almost 3000 atoms to an entangled Dicke state. The state was reconstructed with a negative-valued Wigner function --- an important hallmark of non-classicality. &  \cite{bib:mcconnell2015entanglement} \\
		\hline
		In 2010, two ensembles was entangled by storage of two entangled light fields; and ten years later, four quantum memories was entangled via spin wave. & \cite{bib:lukin2000entanglement, bib:choi2010entanglement} \\
		\hline
		Bose-Einstein condensate was used to create large ensembles of up to ${10^4}$ pair-correlated atoms with an interferometric sensitivity $-1.61$ decibels beyond the shot noise limit. & \cite{bib:lucke2011twin} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Notable developments in atomic ensembles.} \label{tab:atomic_ensembles}
\end{table*}

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		Spontaneous emission from trion (the simplest charged excitons) state prepares a single electron spin in the quantum dot, while spin-photon entanglement was generated from such decay. &  \cite{bib:de2012quantum, bib:gao2012observation} \\
		\hline
	    Two-photon polarisation-entangled states can be generated from biexciton-exciton cascade radiative decay in a single quantum dot. The entangled photon pairs simultaneously show high purity of 0.004, high fidelity of 0.81, high two-photon interference visibilities of 0.86 and on-demand generation efficiency of 0.86. & \cite{bib:muller2014demand} \\
		\hline
		A family of pyramidal site-controlled quantum dots was used to construct an array of entangled photon emitters with fidelities as high as 0.72. & \cite{bib:juska2013towards, bib:mohan2010polarization} \\
		\hline
		A cluster state of entangled five sequential photons was generated by periodic timed excitation of a matter qubit . In each period, an entangled photon is added to the cluster state formed by the matter qubit and the previously emitted photons. & \cite{bib:schwartz2016deterministic} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Major developments with quantum dots.} \label{tab:quantum_dots}
\end{table*}

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		There are three basic types of superconducting qubits --- charge, flux and phase. In 2007, a charge-insensitive qubit, named transmon, was designed.  &  \cite{bib:koch2007charge} \\
		\hline
		 Transmon qubit in a waveguide cavity, named circuit QED, has reached a coherence time on the order of 0.1 ms. & \cite{bib:paik2011observation, bib:rigetti2012superconducting} \\
		\hline
		In 2013, Martinis and his colleagues designed a cross-shaped transmon qubits, named Xmons, which balances coherence, connectivity and fast control. In 2014, they constructed a 5-qubit GHZ state using five Xmons arranged in a linear array. In 2015, they reported the protection of states from environmental bit-flip errors in a nine Xmon qubit linear array. &  \cite{bib:barends2013coherent, bib:barends2014superconducting, bib:kelly2015state} \\
		\hline
		Pan and his colleagues reported the preparation and verification of a genuine 10- and 12-qubit entanglement in a superconducting processor. & \cite{bib:gong2018genuine, bib:song201710} \\		
		\hline
		An 100-photon Schr{\"o}dinger cat state was created mapping from an arbitrary transmon qubit state, and extended to superposition of up to four coherent states. & \cite{bib:vlastakis2013deterministically} \\
		\hline
		In 2016, the lifetime of microwave photon was extended to 0.3 ms with error correction in superconducting circuits. &  \cite{bib:ofek2016extending} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Developments in superconducting rings for quantum information processing.} \label{tab:superconducting}
\end{table*}

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		\textit{Single photon avalanche diodes (SPAD) ---}
		SPADs are the most compact and common single-photon detectors in the world. Commercially Silicon SPADs are available with detection efficiency around 60\% at 780 nm, maximum count rate of 25 MHz and dark count rate as low as 25 Hz. Several remarks are listed as following:

@@

		\end{itemize} &  \cite{bib:shentu2013ultralow} \\
		\hline
		\textit{Superconducting nanowire single photon detectors (SNSPD) ---} 
		They are more efficient, but larger and more expensive than SPADs. Up until now, the highest detection efficiency of SNSPDs is 93\% at 1550nm, demonstrated in 2014. SNSPDs are commercially available with peak detection efficiencies higher than 80\% around 800 nm, maximum dark-count rates of $100\sim 300$ Hz, and a dead-time of $10\sim 70$ns. Similar performance is expected for optimised SNSPD at other wavelengths ($780\sim 1550$ nm). However, SNSPDs must be operated at cryogenic temperatures of a few Kelvin to maintain the superconducting state. This is the main reason why SNSPDs are much more cumbersome and expensive than SPADs. &  \cite{bib:marsili2013} \\
		\hline
		\textit{Transition edge sensors (TES) ---}
		They own the highest detection efficiency, even 98\% (95\%) at wavelengths around 850 nm (1556 nm) have been reported. Moreover, they are photon-number-resolving, owing to the linear response between resistance and temperature. However, the typical thermal recovery times of TESs are a fraction of a microsecond, limiting their application in high-speed quantum network. Besides, TESs usually work in an ultra-low temperature of 100 mK, which makes it challenging to migrate the technique from lab to market. & \cite{bib:fukuda2011, bib:lita2008} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Some state-of-the-art single-photon detectors.}\label{tab:photodetection}
\end{table*}

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		Trapped atoms/ions: A register of 20 individually controlled qubits was generated and characterised; Single-qubit gates with an error per gate of $3.8 \times {10^{ - 5}}$, and deterministic two-qubit gate with a gate error of $8 \times {10^{ - 4}}$; 14-qubit entanglement with a 2-qubit fidelity of 98.6\%. & \cite{bib:friis2018observation, bib:Gaebler2016, bib:monz2011} \\
		\hline
		Nuclear magnetic resonance: 12-qubit system with the simulated fidelity over 99.7\% on each qubit; The average fidelity of 87.5\% on a 7-qubit entangling gate. & \cite{bib:Negrevergne2006, bib:lu2017enhancing, bib:Lu2015} \\
		\hline
		Linear optics: A fully programmable 2-qubit quantum processor with an average quantum process fidelity of 93.2\%. & \cite{bib:qiang2018large} \\
		\hline
		Boson-sampling: Several five-photon boson sampling machines were built and beat early classical computers. & \cite{bib:zhong201812, bib:wang2018toward, bib:wang2017high} \\
		\hline
		Coherent Ising machine: An optical processing approach was used to model and optimise 2000-node optimisation problems based on a network of coupled optical pulses in a ring fibre. & \cite{bib:mcmahon2016fully, bib:inagaki2016coherent} \\
		\hline
		Superconductors: 9-qubit system with an average single-qubit gate fidelity of 99.92\% and a 2-qubit gate fidelity of up to 99.4\%. & \cite{bib:kelly2015state, bib:barends2014superconducting} \\
		\hline
		Spins in Silicon: A programmable 2-qubit quantum processor in silicon with state fidelities of 85 $\sim$ 89\%; 2-qubit CNOT gate; An addressable single-qubit with a control fidelity of 99.6\%. & \cite{bib:watson2018programmable, bib:veldhorst2015two, bib:veldhorst2014addressable}. \\
		\hline
		Nitrogen-vacancy centres: A programmable 2-qubit solid-state quantum processor at room temperature. & \cite{bib:wu2018programmable} \\
		\hline
		Adiabatic quantum computation: A 2048-qubit D-Wave quantum processor was used to predict phase transitions and topological phenomena. & \cite{bib:harris2018phase, bib:king2018observation} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Major milestones in the development of quantum computation.} \label{tab:quantumcomputer}
\end{table*}

>>>>

Optical waveguides can be miniaturised and integrated onto a small chip, which is alignment-free, compact, and phase-stable\index{Phase!Stability}.

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		Atom-light interaction currently represents the most mature method to create atomic squeezing, and owns the highest squeezing of 20.1 dB via an optical-cavity-based measurement. & \cite{bib:hosten2016measurement} \\
		\hline
		The detection of a single photon prepares almost 3000 atoms to an entangled Dicke state. The state was reconstructed with a negative-valued Wigner function -- an important hallmark of non-classicality. &  \cite{bib:mcconnell2015entanglement} \\
		\hline
		In 2010, two ensembles was entangled by storage of two entangled light fields; and ten years later, four quantum memories was entangled via spin wave. & \cite{bib:lukin2000entanglement, bib:choi2010entanglement} \\
		\hline
		Bose-Einstein condensate was used to create large ensembles of up to ${10^4}$ pair-correlated atoms with an interferometric sensitivity $-1.61$ decibels beyond the shot noise limit. & \cite{bib:lucke2011twin} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Notable developments in atomic ensembles.} \label{tab:atomic_ensembles}
\end{table*}

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		Spontaneous emission from a trion (the simplest charged excitons) state prepares a single electron spin in the quantum dot, while spin-photon entanglement was generated from such decay. &  \cite{bib:de2012quantum, bib:gao2012observation} \\
		\hline
	    Two-photon polarisation-entangled states can be generated from biexciton-exciton cascade radiative decay in a single quantum dot. The entangled photon pairs simultaneously show high purity of 0.004, high fidelity of 0.81, high two-photon interference visibilities of 0.86 and on-demand generation efficiency of 0.86. & \cite{bib:muller2014demand} \\
		\hline
		A family of pyramidal site-controlled quantum dots was used to construct an array of entangled photon emitters with fidelities as high as 0.72. & \cite{bib:juska2013towards, bib:mohan2010polarization} \\
		\hline
		A cluster state of entangled five sequential photons was generated by periodic timed excitation of a matter qubit . In each period, an entangled photon is added to the cluster state formed by the matter qubit and the previously emitted photons. & \cite{bib:schwartz2016deterministic} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Major developments with quantum dots.} \label{tab:quantum_dots}
\end{table*}

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		There are three basic types of superconducting qubits -- charge, flux and phase. In 2007, a charge-insensitive qubit, named transmon, was designed.  &  \cite{bib:koch2007charge} \\
		\hline
		 Transmon qubit in a waveguide cavity, named circuit QED, has reached a coherence time on the order of 0.1 ms. & \cite{bib:paik2011observation, bib:rigetti2012superconducting} \\
		\hline
		In 2013, Martinis and his colleagues designed a cross-shaped transmon qubits, named Xmons, which balances coherence, connectivity and fast control. In 2014, they constructed a 5-qubit GHZ state using five Xmons arranged in a linear array. In 2015, they reported the protection of states from environmental bit-flip errors in a nine Xmon qubit linear array. &  \cite{bib:barends2013coherent, bib:barends2014superconducting, bib:kelly2015state} \\
		\hline
		Pan and his colleagues reported the preparation and verification of a genuine 10- and 12-qubit entanglement in a superconducting processor. & \cite{bib:gong2018genuine, bib:song201710} \\		
		\hline
		An 100-photon Schr{\"o}dinger cat state was created mapping from an arbitrary transmon qubit state, and extended to superposition of up to four coherent states. & \cite{bib:vlastakis2013deterministically} \\
		\hline
		In 2016, the lifetime of microwave photon was extended to 0.3 ms with error correction in superconducting circuits. &  \cite{bib:ofek2016extending} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Developments in superconducting rings for quantum information processing.} \label{tab:superconducting}
\end{table*}

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		\textit{Single photon avalanche diodes (SPAD) --}
		SPADs are the most compact and common single-photon detectors in the world. Commercially Silicon SPADs are available with detection efficiency around 60\% at 780 nm, maximum count rate of 25 MHz and dark count rate as low as 25 Hz. Several remarks are listed as following:

@@

		\end{itemize} &  \cite{bib:shentu2013ultralow} \\
		\hline
		\textit{Superconducting nanowire single photon detectors (SNSPD) --} 
		They are more efficient, but larger and more expensive than SPADs. Up until now, the highest detection efficiency of SNSPDs is 93\% at 1550nm, demonstrated in 2014. SNSPDs are commercially available with peak detection efficiencies higher than 80\% around 800 nm, maximum dark-count rates of $100\sim 300$ Hz, and a dead-time of $10\sim 70$ns. Similar performance is expected for optimised SNSPD at other wavelengths ($780\sim 1550$ nm). However, SNSPDs must be operated at cryogenic temperatures of a few Kelvin to maintain the superconducting state. This is the main reason why SNSPDs are much more cumbersome and expensive than SPADs. &  \cite{bib:marsili2013} \\
		\hline
		\textit{Transition edge sensors (TES) --}
		They own the highest detection efficiency, even 98\% (95\%) at wavelengths around 850 nm (1556 nm) have been reported. Moreover, they are photon-number-resolving, owing to the linear response between resistance and temperature. However, the typical thermal recovery times of TESs are a fraction of a microsecond, limiting their application in high-speed quantum network. Besides, TESs usually work in an ultra-low temperature of 100 mK, which makes it challenging to migrate the technique from lab to market. & \cite{bib:fukuda2011, bib:lita2008} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Some state-of-the-art single-photon detectors.}\label{tab:photodetection}
\end{table*}

@@

\begin{table*}[!htbp]
	\begin{tabular}{|p{0.755\linewidth}|p{0.22\linewidth}|}
		\hline
		Summary & References \& years \\
		\hline \hline
		Trapped atoms/ions: A register of 20 individually controlled qubits was generated and characterised; Single-qubit gates with an error per gate of $3.8 \times {10^{ - 5}}$, and deterministic 2-qubit gate with a gate error of $8 \times {10^{ - 4}}$; 14-qubit entanglement with a 2-qubit fidelity of 98.6\%. & \cite{bib:friis2018observation, bib:Gaebler2016, bib:monz2011} \\
		\hline
		Nuclear magnetic resonance: 12-qubit system with the simulated fidelity over 99.7\% on each qubit; The average fidelity of 87.5\% on a 7-qubit entangling gate. & \cite{bib:Negrevergne2006, bib:lu2017enhancing, bib:Lu2015} \\
		\hline
		Linear optics: A fully programmable 2-qubit quantum processor with an average quantum process fidelity of 93.2\%. & \cite{bib:qiang2018large} \\
		\hline
		Boson-sampling: Several five-photon boson sampling machines were built and beat early classical computers. & \cite{bib:zhong201812, bib:wang2018toward, bib:wang2017high} \\
		\hline
		Coherent Ising machine: An optical processing approach was used to model and optimise 2000-node optimisation problems based on a network of coupled optical pulses in a ring fibre. & \cite{bib:mcmahon2016fully, bib:inagaki2016coherent} \\
		\hline
		Superconductors: 9-qubit system with an average single-qubit gate fidelity of 99.92\% and a 2-qubit gate fidelity of up to 99.4\%. & \cite{bib:kelly2015state, bib:barends2014superconducting} \\
		\hline
		Spins in Silicon: A programmable 2-qubit quantum processor in silicon with state fidelities of 85 $\sim$ 89\%; 2-qubit CNOT gate; An addressable single-qubit with a control fidelity of 99.6\%. & \cite{bib:watson2018programmable, bib:veldhorst2015two, bib:veldhorst2014addressable}. \\
		\hline
		Nitrogen-vacancy centres: A programmable 2-qubit solid-state quantum processor at room temperature. & \cite{bib:wu2018programmable} \\
		\hline
		Adiabatic quantum computation: A 2048-qubit D-Wave quantum processor was used to predict phase transitions and topological phenomena. & \cite{bib:harris2018phase, bib:king2018observation} \\
		\hline
	\end{tabular}
	\captionspacetab \caption{Major milestones in the development of quantum computation.} \label{tab:quantumcomputer}
\end{table*}

### 2018-12-28 Sections/the_quantum_space_race.tex
Formatting update

However, extending to longer distances has been problematic. Photon loss in free-space links is affected by weather\index{Weather conditions} conditions and other atmospheric effects\index{Atmospheric effects}\index{Photon loss}, such as pollution\index{Pollution}, which degrade visibility. The Earth's curvature\index{Earth curvature} provides an absolute upper limit, depending on the elevation of the source and receiver. For example, for an observer on a 30m tower, the horizon is at a distance of 20km, a relatively short distance. The observatory used in the experiments performed by the experiments of \cite{bib:NP_3_481, bib:Nat_489_269} were at an elevation of 2393m, allowing transmission over a distance of 143km.

@@

The other important piece of technology is the acquisition, pointing, and tracking technology\index{Acquisition}\index{Pointing}\index{Tracking}, which allows the ground stations to track the location of the satellite as it moves across the sky (which is very rapid for LEO), and vice versa. This is achieved using lasers at separate wavelengths, and allows the photon transmission and the ground-based receivers to be pointing to each other to within $\sim 1.2$mrad \cite{bib:yin2017satellite}. The major aims of the project are to: perform QKD\index{Quantum key distribution (QKD)} between Xinglong and Urumqi (a ground distance of 2,500km); test Bell's inequality\index{Bell!Inequality} across a distance of 1,200km; and perform QST\index{Quantum state teleportation} between the satellite and Ali in Tibet (see Fig.~\ref{fig:space_4}). The final aim is to perform QKD between Beijing and Vienna (a distance of 7,500km that extends well beyond the Earth's curvature).

@@

The second experiment performed ground-to-satellite\index{Ground-to-satellite communication} QST\index{Quantum state teleportation} \cite{bib:ren2017ground}. Here a single polarisation-encoded photon defines the qubit to be teleported, and the satellite acts as the receiver. The entangled photons are generated on the ground, at the observatory in Ngari, Tibet. As with the first experiment described above, the satellite is in LEO and sweeps across the sky, creating a narrow time-window during which the teleportation must be achieved. The longest distance for successful teleportation was $\sim 1400$km, when the satellite emerges from the horizon. When directly overhead, the satellite is at a distance of $\sim 500$km. As Fig.~\ref{fig:space_4}(c) shows, the fidelity of the types of states teleported are all above the theoretical classical bound of $2/3$, with an average of $0.80 \pm 0.01$.

>>>>

However, extending to larger distances has been problematic. Photon loss in free-space links is affected by weather\index{Weather conditions} conditions and other atmospheric effects\index{Atmospheric effects}\index{Photon loss}, such as pollution\index{Pollution}, which degrade visibility. The Earth's curvature\index{Earth curvature} provides an absolute upper limit, depending on the elevation of the source and receiver. For example, for an observer on a 30m tower, the horizon is at a distance of 20km, a relatively short distance. The observatory used in the experiments performed by the experiments of \cite{bib:NP_3_481, bib:Nat_489_269} were at an elevation of 2393m, allowing transmission over a distance of 143km.

@@

The other important piece of technology is the acquisition, pointing, and tracking technology\index{Acquisition}\index{Pointing}\index{Tracking}, which allows the ground stations to track the location of the satellite as it moves across the sky (which is very rapid for LEO), and vice versa. This is achieved using lasers at separate wavelengths, and allows the photon transmission and the ground-based receivers to be pointing to each other to within $\sim 1.2$mrad \cite{bib:yin2017satellite}. The major aims of the project are to:
\begin{itemize}
\item Perform QKD\index{Quantum key distribution (QKD)} between Xinglong and Urumqi (a ground distance of 2,500km).
\item Test Bell's inequality\index{Bell!Inequality} over a distance of 1,200km.
\item Perform quantum state teleportation\index{Quantum state teleportation} between the satellite and Ali in Tibet (see Fig.~\ref{fig:space_4}).
\item (Ultimate goal) Perform QKD between Beijing and Vienna (a distance of 7,500km that extends well beyond the Earth's curvature).
\end{itemize}

@@

The second experiment performed ground-to-satellite\index{Ground-to-satellite communication} QST\index{Quantum state teleportation} \cite{bib:ren2017ground}. Here, a single polarisation-encoded photon defines the qubit to be teleported, and the satellite acts as the receiver. The entangled photons are generated on the ground, at the observatory in Ngari, Tibet. As with the first experiment described above, the satellite is in LEO and sweeps across the sky, creating a narrow time-window during which the teleportation must be achieved. The longest distance for successful teleportation was $\sim 1400$km, when the satellite emerges from the horizon. When directly overhead, the satellite is at a distance of $\sim 500$km. As Fig.~\ref{fig:space_4}(c) shows, the fidelity of the types of states teleported are all above the theoretical classical bound of $2/3$, with an average of $0.80 \pm 0.01$.
